%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Software Engineer - Working student} % Job title
    {FNT Software} % Organization
    {Ellwangen, Germany} % Location
    {Mar. 2021 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built an integration between the configuration management database FNT Command and Atlassians JIRA.}
        \item {Migrate use cases from "old" FNT ServiceEngine to FNT ProcessCenter by recreating most of the demo workflows and by developing a JEE microservice that fills the gaps to fully migrate to ProcessCenter.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Compulsory Internship} % Job title
    {FNT Software} % Organization
    {Ellwangen, Germany} % Location
    {Sep. 2020 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of a Node.js microservice that expands the capabilities of FNT ServiceEngine (process management solution) by implementing service-tasks for the workflow and decision automation platform Camunda and the projects forms domain.}
        \item {Increased efficiency in pre-sales by developing a project that simplifies the creation of demo cases and extends the currently possible capabilities.}
        \item {Created multiple end-to-end use cases for the FNT ServiceEngine to further enable the pre-sales team in customer presentations/requests.}
        \item {Testing of business intelligence solution FNT Analytics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student Assistant - Software Engineer} % Job title
    {Institute for Materials Research @ Aalen Univeristy} % Organization
    {Aalen, Germany} % Location
    {Mar. 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a proof-of-concept controlling software for ZEISS Axio Imager Vario light microscopes in C\#}
      \end{cvitems}
    }

  \cventry
    {Software Developer} % Job title
    {Freelance Work} % Organization
    {Heidenheim, Germany} % Location
    {Mar. 2017 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created small projects that got commissioned through users in online forums}
        \item {Connected with other developers and started to work on a cloud native game-server hosting platform}
        \item {Joined a team of local students and developed a React Native proof-of-concept app for the city of Heidenheim}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
